\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-10-13 paper.tex

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}
\notaL{Si quieres ponerme algún comentario en el manuscrito usa el
  comando notaC, similar al comando notaL que uso yo}
\section{Introduction}
\label{sec:introduction}
\notaL{Debiste poner etiquetas en todas las subsecciones y secciones, y
  ecuaciones y figuras.}
\notaL{No entiendo nada de la introducción}
The structural properties of nanostructured materials  has  received a
considerable attention,  and a large research effort has been devoted
to them \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PS) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PS the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN \notaL{Define acrónimos antes de
  usarlos}. optical elements from PS
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

The paper is organized as follows. In Section 2  we report the effect
of how the current density can be calculated from an electrostatic
model for photonic crystals with gradient refractive index (EMPCGRIN),
demonstrating that there is a direct relation of the gradient
generated by the electrode when it attacks the Silicon sample, we can
see the depth of the structure and its porosity, in each of the
measuring points. In Subsection 2.2 we present a formalism based on
the methods used for the analysis of photonic crystal structures is
the transfer matrix method. We use it to investigate the reflectance
of light in a one-dimensional photonic crystal. In Section 3 we
provide experimental  details about the manufacture of PS dielectric
multilayers and Section 4 we shows the comparison of numerical and
experimental results followed. Finally,  the conclusions given in
Section. 5 \notaL{Checar que esto corresponda a lo que sigue del
  artículo}

>>>>

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}

\notaV{Surfaces with gradient in refractive index has attracted attention due
 ti its ability to unpair the relation between the shape of the optical 
lens with its optical response. In spite of its possible usage in 
different kinds of devices and applications, it still remains
desirable to predesign GRIN structures with spacial predictability 
of electrochemical gradients.  In this work we report}

\section{Introduction}
\label{sec:introduction}
\notaV{$
Introduction

Surfaces with gradient in the refractive index (GRIN) are of 
importance not only due to the possibility of being able to 
engineer/tune the propagation of light within the structure’s 
surface for applications such as flat lenses, but also for several 
interesting biological applications where the continual topographical 
variation is being exploited [X]. As an example, roughness dependent 
response of the cells has been tested on such materials for applications 
in medical implants [Y].   Gradients have also been employed for several 
technological applications such as high-yield screening of catalysts, 
sensing materials and biomolecules [W. F. Maier, K. Stçwe, S. Sieg, Angew. 
Chem. 2007, 119, 6122; Angew. Chem. Int. Ed. 2007, 46, 6016. ;  S. Jayaraman, 
A. C. Hillier, J. Comb. Chem. 2004, 6, 27; S. Jayaraman, A. C. Hillier, Meas. 
Sci. Technol. 2005, 16, 5. ; R. A. Potyrailo, V. M. Mirsky, Chem. Rev. 2008, 108, 770.]

Apart from some methods developed by S.E. Fosdick et al [JACS  2010, 132, 9226-9227], 
synthesis of  Ag-Au alloy gradients on steel and chemical composition gradients of CdS 
on gold electrode have been made by Shannon’s group[].  Among the electrochemical methods, 
compositional and doping density changes in the conducting polymer have been used to 
produce the gradients using Indium tin oxide electrode [S. Inagi, Y. Ishiguro et al 
Angew Chem Int. Ed. 2010, 49, 10136-10139; Angew Chem 2010 122, 10334-10337].   
Electrochemically induced potential gradients have been shown to catalyze the 
reactions and gradient doping of the polymers [Gradient Doping of Conducting Polymer 
Films by Means of Bipolar Electrochemistry Y. Ishiguro, S. Inagi, and T.Fuchigami 
Langmuir 2011 27 (11), 7158-7162].   (PENDING : few MORE EXAMPLES from last couple of years)
As compared to the above mentioned techniques, a relatively economical, 
fast and easy approach with an additional advantage of being compatible 
with VLSI devices & integrable with microelectronics, for the fabrication 
of refractive index (pore size) gradient has been the development of asymmetric 
electrode configuration in the electrochemical synthesis of porous silicon [].  
Although porous silicon initially stimulated the interest of the scientific 
community due to visible PL at room temperature, presently it has 
been accepted as a multifaceted optical material due to its large surface 
area, biocompatibility, ease of fabrication and tunable refractive index. 
Porous silicon emanating applications now cover various fields such as 
chemical and biosensor [Porous Silicon Fabry–Pérot Interferometer for
N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar, 
Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI: 
10.1021/acssensors.0c00348], microelectronics and MEMS[xx], as well as a 
range of optical[XXX] and optoelectronic applications[XXX].  Specifically, 
the temporal variation of current density results in the variation of 
porosity along the depth for the easy fabrication of different kinds 
[xxX] of 1D photonics crystals. 
Although the conventional fabrication of PS requires laterally 
homogeneous samples (with same structural characteristics on the 
porous surface), asymmetric configuration to produce porous silicon 
with a lateral gradient (in terms of optical thickness/ pore size and t
hickness of the porous layer) has also been exploited for different applications 
[REF… ]. In this configuration, a small platinum electrode (cathode)  
is positioned perpendicular  to the surface of the Si substrate (anode) 
at one end or the center  of the cell, resulting  in a decrease in current 
density  with an increase in the distance from the electrode \cite{I102, I103}. 
The resulting porous surface can have pore sizes ranging from a few nanometers  
to  few micrometers  \cite{I104}. The range of the dimensions of the pores and 
the corresponding  thickness obtained on the same chip can be controlled by 
adjusting the location of the pin/circular electrode,  anodizing current density
and etching time period for a given silicon wafer.   Sailor Group 
in 2002 \cite{I101} applied it for the determination of protein size. 
Additionally, due to the biocompatible nature of PS, possible gating of 
the optical response by variation in pH of the solution was shown to 
trap/release the biomolecule for possible drug delivery applications. 
 Similar asymmetric electrode configuration was used to fabricate 
 optical filters (multilayered structures) with lateral gradient 
 [Li, Yang Yang, Peter Kim, and Michael J. Sailor. 
 "Painting a rainbow on silicon–a simple method to 
 generate a porous silicon band filter gradient.
 " physica status solidi (a) 202.8 (2005): 1616-1618.] for 
 developing ethanol sensor (Sailor 2012...). Additionally it 
 has been shown that the combination of thermal  oxidation  and 
 infiltration of TiO2  by ALD offers the  opportunity to manufacture 
a high refractive indices contrast in visibly transparent GRIN 
optical elements from PS \cite{I16}.    Kruger et al showed 
the ...  [ Krueger, Neil A., et al. "Porous silicon gradient 
refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.] 
In addition the same group ...[Krueger, Neil A., et al. 
 "Electrochemical Fabrication of Flat, Polymer‐Embedded 
Porous Silicon 1D Gradient Refractive Index Microlens 
Arrays." physica status solidi (a) 215.13 (2018): 1800088].  
Recently, J Wang et al. has shown the fabrication of 
miniature spectrometer with PS based rugate filter using 
radial interfacial potential distribution (Wang, Joanna, 
Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral 
gradient rugate in porous silicon for a miniature spectrometer
application." ChemElectroChem 6.24 (2019): 5967-5972. On the other 
hand, the effect of different topographical features present on the 
same chip, has also been used to culture / adhesion of certain cells \cite{I14}
In the investigation of such practically applicable systems, 
the spacial predictability of electrochemical gradients can 
be useful for predesigning the devices for different applications.  
In this work, we report a simple analytical model to quantitatively 
analyze the gradient (calculate the porosity /current density and 
thickness) at any point of the GRIN structure.  The paper is organized 
as follows. In Section 2  we report a simple analytical model to calculate 
the current density/porosity and thickness  at any point of the GRIN structure. 
The model contemplates (Dr. Mochan) the formation of electrochemically generated 
porous surface  (applicable/extendible to photonic crystals with lateral gradient) 
with lateral gradient in refractive index  ...with predictable  depth and porosity 
at any point on surface.   In Section 3 we provide experimental details for the 
synthesis of porous silicon samples with lateral refractive index gradient.  
Section 4 includes experimental results and its comparison with numerically 
evaluated parameters . Finally,  the conclusions are given in Section X

$}

\notaV{$ Painting a rainbow on silicon - A simple method to 
\notaV{generate a porous silicon 
band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
In: Physica Status Solidi (A) Applications and Materials Science, 
Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)

Electrochemical Preparation of Pore Wall Modification Gradients 
across Thin Porous Silicon Layers
Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski, 
Michael J. Sailor, and Gordon M. Miskelly
Langmuir 2010 26 (10), 7598-7603
DOI: 10.1021/la904408h

 Richardson, Kathleen A., et al. "Advances in infrared gradient 
 refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.

Lavanant, Enora, et al. "Radial gradient refractive index 
(GRIN) infrared lens based on spatially resolved crystallization 
of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
While widely used in the visible, radial gradient refractive 
index (GRIN) lenses are still elusive in the IR waveband. 
In this paper we introduce a new method based on spatially
resolved crystallization of chalcogenide glass to produce such lenses. 
Optical and structural

Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass 
with Gradient Refractive Index for Ultralow Diffuse Reflectance 
and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
Nanostructured glass with subwavelength hollow nanopillars 
of diameters of sub-65 nm was fabricated, showing high optical 
transmittance and ultralow diffuse reflectance. A simple
process involving single-step plasma etching was used on a 
glass slide coated with a SiO2...

Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman. 
"Patterning Refractive Index on the Surface of a Chip by Direct 
Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.

Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a 
Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.

Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
 "Patterning Refractive Index on the Surface of a Chip by Direct 
 Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.

$
}
